\begin{thebibliography}{9}
\bibitem{Android ADK Arduino}{}
Mario Böhmer
\emph{Beginning Android ADK with Arduino}. \\
\url{http://books.google.se/books/about/Beginning_Android_ADK_with_Arduino.html?id=c8QwhM9DyhcC&redir_esc=y}
\\
hämtad 2013-01-15.

\bibitem{Motraxx_XFLY400-12}{}
Motraxx,
\emph{Motraxx XFLY400-12}. \\
\url{http://files.voelkner.de/225000-249999/238829-da-01-ml-Elektromotor_XFLY400
_12_de_en.pdf}
\\ hämtad 2013-01-13.
\bibitem{Delta_BFB1212VH-R00}{}
Delta,
\emph{BFB1212VH-R00 (BFB120x120x32mm)},\\
\url{http://www.delta.com.tw/product/cp/dcfans/download/pdf/BFB/
BFB120x120x32mm.pdf}
\\ hämtad 2013-01-13.

\bibitem{Protocol buffer}{}
Google,
\emph{Protocol Buffers – Google's data interchange format – Google Project
Hosting}, \\
\url{http://code.google.com/p/protobuf/} \\
hämtad 2012-12-10.

\bibitem{Nanopb}{}
Petteri Aimonen,
\emph{Nanopb - protocol buffers with small code size}, \\
\url{http://koti.kapsi.fi/jpa/nanopb/} \\
hämtad 2012-12-10.

\bibitem{Source code}{}
Daniel Josefsson et al.,
\emph{Källkod för svävare}, \\
\url{https://github.com/jenmo917/TNE085} \\
hämtad 2013-01-15.

\bibitem{AOAA}{}
Embedded Artists,
\emph{Android Open Accessory Application Kit}, \\
\url{http://www.embeddedartists.com/products/app/aoa_kit.php} \\
hämtad 2013-01-14.

\bibitem{Arduino ADK}{}
Arduino,
\emph{ADK}, \\
\url{http://arduino.cc/en/Main/ArduinoBoardADK} \\
hämtad 2013-01-14.

\bibitem{Eclipse_ArduinoCore}{}
Arduino,
\emph{Arduino för Eclipse}, \\
\url{http://playground.arduino.cc/code/eclipse} \\
hämtad 2013-01-15.

\bibitem{USBHost}{}
Arduino,
\emph{USB\_Host Library}, \\
\url{http://labs.arduino.cc/ADK/AccessoryMode} \\
hämtad 2013-01-14.

\bibitem{Wire}{}
Arduino,
\emph{Wire Library}, \\
\url{http://arduino.cc/en/Reference/Wire} \\
hämtad 2013-01-14.

\bibitem{Eventsystem}{}
mromani, Arduino forum user,
\emph{Event System}, \\
\url{http://arduino.cc/forum/index.php/topic,37650.0.html} \\
hämtad 2013-01-14.

\bibitem{kompass}{}
Sparkfun,
\emph{Kompassmodul}, \\
\url{https://www.sparkfun.com/products/7915} \\
hämtad 2013-01-14.

\bibitem{ITead Studio}{}
ITead Studio,
\emph{PCB Manufactor}, \\
\url{http://imall.iteadstudio.com} \\
hämtad 2013-01-15.

\bibitem{MVC}{}
Wikipedia,
\emph{Model-View-Controller}, \\
\url{http://en.wikipedia.org/wiki/Model-view-controller} \\
hämtad 2013-01-15.

\bibitem{Android Reference}{}
Google,
\emph{Android Reference}, \\
\url{http://developer.android.com/reference/} \\
hämtad 2013-01-15.
\end{thebibliography}
